--
title: "Lab 2 Social media experiments"
output: html_document
author: Florian Foos
---

# Step 1: Change the root directory

```{r setup, include=FALSE, cache=FALSE}


rm(list=ls())
require("knitr")
knitr::opts_knit$set(root.dir = "~/Foos Lab Dropbox/Florian Foos/Social-Media-Experiments/Lab2") 

getwd()
```

# Step 2: Load packages

```{r libraries, include=FALSE, cache = FALSE}
library(tidyverse)
library(estimatr)
library(texreg)
library(randomizr)
library(ri2)

```


# Step 3: Reading in your data frame


```{r readdata, echo=FALSE}

df_postcode<-read.csv(file = "Data/Postcode_Registration.csv")

```

# Step 4: Explore your data frame

What are the outcome and treatment variables? Which is the cluster variable?

```{r explore1, echo=FALSE}

names(df_postcode)

df_postcode %>% head()
```

# Step 5: Analysis 

First regress the number of registered voters per postcode on the treatment assignment indicator ("register") without accounting for clustering at the postcode sector level (wrong).

Then regress the number of registered voters per postcode on the treatment assignment indicator ("register") while accounting for clustering at the postcode sector level (correct).


```{r explore2, echo=FALSE}

se_naive <- lm_robust(n_nomiss~register +Constituency, data=df_postcode)  %>% extract.lm_robust(include.ci = FALSE)

clustered_se <- lm_robust(n_nomiss~register +Constituency, clusters = ps, data=df_postcode)  %>% extract.lm_robust(include.ci = FALSE)

texreg(list(se_naive, clustered_se), include.ci = FALSE, omit.coef = "Constituency", caption =
         "Effect on registrations at postcode level (excluding missing sectors)", digits=4)

```


# Exercise 5A. 

Use n_young_withmiss (registrations where age < 30 years) as the outcome variable.

Regress n_young_withmiss on register, first without clustering your standard errors, then when clustering your standard errors at the postcode sector level. 

Interpret your results: What happens to the standard error once you cluster at the potcode sector level?


```{r analysis_ex, echo=FALSE}



```


# Step 6: Cluster random assignment 

Perform cluster random assignment with randomizr 

Re-assign subject by cluster to treatment and control, first into two conditions, then into three conditions:

```{r assign, echo=FALSE}

?cluster_ra

df_postcode %>% count(ps)

cluster_declaration <- declare_ra(N = 717, m=359, clusters=df_postcode$ps) #declare random assignment

cluster_declaration

set.seed(123)

df_postcode <-
  df_postcode %>%
  mutate(
  Postcode = X,  
  cluster_Z = cluster_ra(clusters=df_postcode$ps, m=359),
  cluster_3group = cluster_ra(clusters=df_postcode$ps, m_each=c(239, 239, 239))
  )

df_postcode %>%
  group_by(cluster_Z) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

df_postcode %>%
  group_by(cluster_3group) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

print(df_postcode %>%
  group_by(ps, Postcode) %>% summarise(cluster_Z), n=1000)

print(df_postcode %>%
        group_by(ps, Postcode) %>% summarise(cluster_3group), n=1000)


```

# Exercise 6A. 

Now cluster-randomly assign your postcodes by postcode sector into 4 experimental conditions (Control + 3 Treatment Conditions). Assign 40% of all postcode sectors to control.  

```{r assign_ex, echo=FALSE}



```


