--
title: "Lab 1 Social media experiments"
output: html_document
author: Katharina Lawall
---

# Step 1: Change the root directory

```{r setup, include=FALSE, cache=FALSE}


rm(list=ls())
require("knitr")
knitr::opts_knit$set(root.dir = "C:/Users/katha/Dropbox/Social-Media-Experiments/Lab1") 

getwd()
```

# Step 2: Load packages

```{r libraries, include=FALSE, cache = FALSE}
library(dplyr)
library(randomizr)
library(foreign)
library(estimatr)

```


# Step 3: Reading in data


```{r readdata, echo=FALSE}
data<-read.csv(file = "Data/data_anonymized_standard_assumption.csv")


```

# Step 4: Explore the data

What are the outcome variables? What are anonymity and log.followers? How many observations are there? 

```{r explore1, echo=FALSE}

data %>% head()
data %>% nrow()
```

What is treat.f? 

```{r explore2, echo=FALSE}

data %>% group_by(treat.f, In_group, high_followers) %>% count()
```

# Step 5: Random assignment

```{r assign, echo=FALSE}



# Simple random assignment to two groups
set.seed(123)

data <- data %>% mutate (assignment_simple = simple_ra(N = nrow(data), num_arms = 2))

data %>% group_by(assignment_simple) %>% count()



# Complete random assignment to two groups
set.seed(123)

data <- data %>% mutate (assignment_complete = complete_ra(N = nrow(data), num_arms = 2))

data %>% group_by(assignment_complete) %>% count()

#Q. What's the difference between simple and complete RA? Why is it important to set a seed? 


```

# Exercise 5A. 

Recreate the random assignment from the Munger experiment. How many treatment and control groups do you need? Are you going to use simple or complete RA? Bonus: can you name the treatment and control groups? 

```{r assign_ex, echo=FALSE}



```

# Step 6: Analysis

```{r analyse, echo=FALSE}
data$treat.f<-as.factor(data$treat.f) # recode as factor

##first model

wk1_rac<-summary(lm_robust(racism.scores.post.1wk ~ treat.f + log.followers +  racism.scores.pre.2mon, data = data))

wk1_rac

##second model looks only at the most anonymous users

wk1_rac_anon<-summary(lm_robust(racism.scores.post.1wk ~ treat.f  + log.followers + racism.scores.pre.2mon, 
                         data = filter(data,anonymity>1) ))

wk1_rac_anon
```


# Exercise 6A. 

Let's estimate a third model for non-anonymous users:  

How do you interpret this? 

```{r analyse_6a, echo=FALSE}





```



# Step 7: Graphs

```{r graphs, echo=FALSE}

wk1_models<-list(wk1_rac)

wk1_modelnames<-list("wk1_rac")



##plot the wk1 models, with axis labels

for (i in 1:length(wk1_models)){
  ##change length, one fewer coefficient
  coefs <- t(t(c(wk1_models[[i]]$coefficients[2:6,1])))
  ses <- t(t(c(wk1_models[[i]]$coefficients[2:6,2])))
  y.axis <- c(1:5)
  #fix x axis to the max values any coefficients take for comparison
  min <- (-.65)
  max <- .55
  var.names <- c("In-Group/Low","Out-Group/Low","In-Group/High","Out-Group/High", "Log Followers")
  adjust <- 0
  ##########################
  ###change filename depending on the data source
  ##########################
  pdf(paste0(wk1_modelnames[i], ".pdf"), 5, 7)
  par(mar=c(4,6,1,1))
  
  plot(coefs[,1], y.axis, type = "p", axes = F, xlab = "Change in Average Daily Slur Use", ylab = "", pch = 19, cex = .8, 
       xlim=c(min,max),ylim = c(.5,5.5), main = "")
  rect(min,.5,max,1.5, col = c("grey97"), border="grey90", lty = 2)
  rect(min,1.5,max,2.5, col = c("grey95"), border="grey90", lty = 2)
  rect(min,2.5,max,3.5, col = c("grey97"), border="grey90", lty = 2)
  rect(min,3.5,max,4.5, col = c("grey95"), border="grey90", lty = 2)
  rect(min,4.5,max,5.5, col = c("grey97"), border="grey90", lty = 2)
  
  axis(1, tick = T,cex.axis = .75, mgp = c(2,.7,0))
  axis(2, at = y.axis, label = var.names, las = 1, tick = FALSE, cex.axis =.8, hadj=1)
  abline(h = y.axis, lty = 2, lwd = .5, col = "white")
  segments(coefs[,1]-qnorm(.975)*ses[,1], y.axis+2*adjust, coefs[,1]+qnorm(.975)*ses[,1], y.axis+2*adjust, lwd =  1)
  
  segments(coefs[,1]-qnorm(.95)*ses[,1], y.axis+2*adjust-.035, coefs[,1]-qnorm(.95)*ses[,1], y.axis+2*adjust+.035, lwd = .9)
  segments(coefs[,1]+qnorm(.95)*ses[,1], y.axis+2*adjust-.035, coefs[,1]+qnorm(.95)*ses[,1], y.axis+2*adjust+.035, lwd = .9)
  points(coefs[,1], y.axis+2*adjust,pch=21,cex=.8, bg="white")
  abline(v=0, lty = 2) # draw dotted line through 0 for reference line for null sign ificance hypothesis testing
  
  

  dev.off()
  
}

```

# Additional material: Exercise 6B. 
Let's estimate all three models for the week 2 outcomes: 

How do you interpret the results? How does this compare to week 1 outcomes?
  
```{r analyse_6b, echo=FALSE}



```

